Flatiron cleaning

### 2021-10-20 Rmd/rdi analysis.Rmd
Fix cleaning and calculation

# `r emo::ji("question_mark")` Reminders of each capping and formula:

@@

**We start with a number of patient who has drug info of `r drugs %>% distinct(patientid) %>% nrow()`.**

@@

  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor))

@@

@@

Patients with part of their first line switched to Adjuvant line because of surgery. How long is this adjuvant line?
```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate, end = lineenddate)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, linenumber, linenumber_new, linenumber_adj, 
         drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= line_duration))+
  geom_bar(color = "slateblue") +
  theme_minimal(base_size = 14)+
  ggforce::facet_zoom(xlim = c(0, 200), zoom.size = 1)

```

@@

### step 10: Code cycle
```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>%

  arrange(patientid, episodedate) %>% 
  group_by(patientid, linenumber_new) %>%
  # Need the number of time of the "major" drug is seen in the line
  mutate(cycle_count_perline = min(drugname_count_perline)) %>%
  mutate(cycle_drugname = case_when(
    cycle_count_perline == drugname_count_perline          ~ drugname,
    TRUE                                                   ~ NA_character_
  )) %>% 
  # select(-drugname_count_perline) %>% 
  group_by(patientid, linenumber_new, cycle_drugname) %>%
  mutate(cycle_inc = row_number(cycle_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------

@@

  # group_by(patientid, linenumber_new, cycle_inc) %>%
  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
  arrange(patientid, episodedate, cycle_inc) %>% 
  group_by(patientid, linenumber_new) %>%
  mutate(cycle_increment = cycle_inc) %>% 
  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
  # cycle date
  group_by(patientid, linenumber_new, cycle_increment) %>% 
  mutate(cycle_start_date = min(episodedate)) %>% 
  # select(patientid, linename, linenumber_new, drugname, episodedate,
  #        cycle_count_perline, cycle_drugname, drugname_count_perline, cycle_increment, cycle_start_date) %>%

  group_by(patientid, linenumber_new) %>% 
  mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
         cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days

  # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
  mutate(n = row_number(drugname)) %>%

  mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
  fill(base_days_between_cycle, .direction = "downup") %>% 
  mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
                                       (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
  # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
  group_by(patientid, linenumber_new) %>%
  mutate(drug_count_perline = n()) %>%
  mutate(skipped_cycle_indays1 = ifelse(
    (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
  )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
  # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
  group_by(patientid) %>% 
  mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
  ungroup()
```

@@

`r emo::ji("check")`  
We decided to take the creatinine, weight, bsa measured within a month and in the same cycle of the administration AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line

```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_creat = case_when(
    (therapy == "Upfront Surgery" &
       interval_creat < 31 &
       creat_date < lineenddate &
       creat_date > surgerydate)                  ~ interval_creat,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_creat < 31 &
           creat_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_creat < 31 &
             creat_date < lineenddate &
             creat_date > surgerydate)
      )                                          ~ interval_creat,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with weight
  left_join(. , weight, by = "patientid") %>%
  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
                        duration(n=1, unit="days"))) %>%
  mutate(interval_weight = case_when(
    (therapy == "Upfront Surgery" &
       interval_weight < 31 &
       weight_date < lineenddate &
       weight_date > surgerydate)                  ~ interval_weight,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_weight < 31 &
           weight_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_weight < 31 &
             weight_date < lineenddate &
             weight_date > surgerydate)
      )                                          ~ interval_weight,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_weight) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
         cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with body_surface_area
  left_join(., body_surface_area, by = "patientid") %>%
  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
                          duration(n=1, unit="days"))) %>%
  mutate(interval_bsa = case_when(
    (therapy == "Upfront Surgery" &
       interval_bsa < 31 &
       bsa_date < lineenddate &
       bsa_date > surgerydate)                  ~ interval_bsa,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_bsa < 31 &
           bsa_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_bsa < 31 &
             bsa_date < lineenddate &
             bsa_date > surgerydate)
      )                                          ~ interval_bsa,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_bsa) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%
  # Calculate more bsa value with height and weight using Du Bois formula
  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
  select(-bsa_du_bois) %>%

  # Merge with auc
  left_join(., areaUC, by = c("patientid", "drugname")) %>%
  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_auc = case_when(
    (therapy == "Upfront Surgery" &
       interval_auc < 31 &
       auc_date < lineenddate &
       auc_date > surgerydate)                  ~ interval_auc,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_auc < 31 &
           auc_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_auc < 31 &
             auc_date < lineenddate &
             auc_date > surgerydate)
      )                                          ~ interval_auc,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_auc) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
    mean_RDI_per_chemotype_drug < 1                  ~ "correct",
    mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
    mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
    mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("correct", "highly underdose", "underdose", "perfect", "higher dose", "overdose")))

Frontline <- Frontline %>% 
  filter(str_detect(drugname, "platin|taxel"))
```
<br>
<br>
<br>

@@

### Number of line in treatment and cycle in frontline (more cleaning needs to be done here)
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
Frontline %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
Frontline %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
Frontline %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Don't forget we have that "neo + surg"
```{r}
Frontline %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

Frontline %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront neo
```{r}
Frontline %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Frontline %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront surgery
```{r}
Frontline %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Frontline %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
<br>

@@

# Frontline %>% filter(is.na(amount)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
# 
# Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
```
If we remove patients who have at least 1 missing amount administered, we lose `r Frontline %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.

If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.

@@

<div class = "row">
<div class = "col-md-6">
```{r treatment survival, fig.height = 7}
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ debulking, data=Frontline %>%
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

@@

ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ 1, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ 1, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of from first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

>>>>

# `r emo::ji("spiral_notepad")` This report is using **actual weight**

# `r emo::ji("spiral_notepad")` Reminders of each capping and formula:

@@

**We start with a number of patient who have drug info of `r drugs %>% distinct(patientid) %>% nrow()`.**

@@

  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
  group_by(patientid, linenumber_new) %>% 
  mutate(linestartdate_new = first(episodedate)) %>% 
  mutate(lineenddate_new = last(episodedate)) %>% 
  ungroup()

@@

`r emo::ji("question_mark")` **Are we keeping the patients who had Neo + surgery without Adjuvant?**

@@

For these patients, I was worried that the part of their first line which was switched to Adjuvant line because of surgery is short... How long is this adjuvant line?
```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, linenumber, linenumber_new, linenumber_adj, 
         drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= line_duration))+
  geom_histogram(color = "slateblue", fill = "grey", binwidth = 7) +
  theme_minimal(base_size = 14)+
  labs(x="Line duration", 
       y="Number of Patient",
       caption = "Each bar represents 7 days, bottom plot is zoomed in")+
  ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)

```
Several patients have a short line.  
`r emo::ji("question_mark")` **Should me remove the patient with a line during less than a cycle

```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, drugname, episodedate, line_duration, 
         chemotherapy_type, therapy, 
         linenumber, linenumber_new, linenumber_adj) %>% 
  filter(line_duration < 30)
```

@@

### step 10: Code cycle
```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>% 
  filter(str_detect(drugname, "taxel|platin")) %>% # Need to that now for patient who got Bev only once per line F02D8628A5394

  arrange(patientid, episodedate) %>% 
  group_by(patientid, linenumber_new) %>%
  # Need the number of time of the "major" drug is seen in the line
  mutate(cycle_count_perline = min(drugname_count_perline)) %>%
  mutate(cycle_drugname = case_when(
    cycle_count_perline == drugname_count_perline          ~ cycle_drugname,
    TRUE                                                   ~ NA_character_
  )) %>% 
  # select(-drugname_count_perline) %>% 
  group_by(patientid, linenumber_new, cycle_drugname) %>%
  mutate(cycle_increment = row_number(cycle_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
  # F01D908A013B7 has more pacli at the end but in the same line

@@

  # group_by(patientid, linenumber_new, cycle_inc) %>%
  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
  arrange(patientid, episodedate, cycle_increment) %>% 
  group_by(patientid, linenumber_new) %>%
  # mutate(cycle_increment = cycle_inc) %>% 
  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
  # cycle date
  group_by(patientid, linenumber_new, cycle_increment) %>% 
  mutate(cycle_start_date = min(episodedate)) %>% 
  # select(patientid, linename, linenumber_new, drugname, episodedate,
  #        cycle_count_perline, cycle_drugname, drugname_count_perline, cycle_increment, cycle_start_date) %>%

  # # CODE FOR SKIPPED CYCLE
  # group_by(patientid, linenumber_new) %>% 
  # mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
  #        cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
  # 
  # # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
  # mutate(n = row_number(drugname)) %>%
  # 
  # mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
  # fill(base_days_between_cycle, .direction = "downup") %>% 
  # mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
  #                                      (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
  # # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
  # group_by(patientid, linenumber_new) %>%
  # mutate(drug_count_perline = n()) %>%
  # mutate(skipped_cycle_indays1 = ifelse(
  #   (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
  # )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
  # # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
  # group_by(patientid) %>% 
  # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
  ungroup()
```

@@

`r emo::ji("check")`  
We decided to take the creatinine, weight, bsa measured within a month of the cycle start date AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line

```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_creat = case_when(
    (therapy == "Upfront Surgery" &
       interval_creat < 31 &
       # creat_date < lineenddate &
       creat_date > surgerydate)                  ~ interval_creat,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_creat < 31 &
           creat_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_creat < 31 &
             # creat_date < lineenddate &
             creat_date > surgerydate)
      )                                          ~ interval_creat,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with weight
  left_join(. , weight, by = "patientid") %>%
  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
                        duration(n=1, unit="days"))) %>%
  mutate(interval_weight = case_when(
    (therapy == "Upfront Surgery" &
       interval_weight < 31 &
       # weight_date < lineenddate &
       weight_date > surgerydate)                  ~ interval_weight,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_weight < 31 &
           weight_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_weight < 31 &
             # weight_date < lineenddate &
             weight_date > surgerydate)
      )                                          ~ interval_weight,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_weight) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
         cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with body_surface_area
  left_join(., body_surface_area, by = "patientid") %>%
  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
                          duration(n=1, unit="days"))) %>%
  mutate(interval_bsa = case_when(
    (therapy == "Upfront Surgery" &
       interval_bsa < 31 &
       # bsa_date < lineenddate &
       bsa_date > surgerydate)                  ~ interval_bsa,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_bsa < 31 &
           bsa_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_bsa < 31 &
             # bsa_date < lineenddate &
             bsa_date > surgerydate)
      )                                          ~ interval_bsa,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_bsa) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%
  # Calculate more bsa value with height and weight using Du Bois formula
  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
  select(-bsa_du_bois) %>%

  # Merge with auc
  left_join(., areaUC, by = c("patientid", "drugname")) %>%
  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_auc = case_when(
    (therapy == "Upfront Surgery" &
       interval_auc < 31 &
       # auc_date < lineenddate &
       auc_date > surgerydate)                  ~ interval_auc,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_auc < 31 &
           auc_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_auc < 31 &
             # auc_date < lineenddate &
             auc_date > surgerydate)
      )                                          ~ interval_auc,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_auc) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
    mean_RDI_per_chemotype_drug < 1                  ~ "correct",
    mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
    mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
    mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("correct", "highly underdose", "underdose", "perfect", "higher dose", "overdose")))
```
<br>
<br>
<br>

@@

### Number of line in treatment and cycle in frontline  
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment) %>% 
  tbl_summary()
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Don't forget we have that "neo + surg"
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront surgery
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
<br>

@@

# Frontline %>% filter(is.na(amount)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
# 
# Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
```
<!-- If we remove patients who have at least 1 missing amount administered, we lose `r Frontline %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.   -->

<!-- If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.   -->

@@

<div class = "row">
<div class = "col-md-6">
```{r treatment survival, fig.height = 7}
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ 1, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ debulking, data=Frontline %>%
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

@@

@@
